\paragraph{Objectives of the DET subproject.}
Below we list the specific objectives of the DET subproject. For definitiveness we assume that the project will run from 2016 to 2018. We denote the quarters of the year as Q1 to Q4. Thus, for example, Q1-16, means first quarter of 2016, while Q1/Q3 means first to third quarter of 2016. 

\begin{enumerate}
\item {\bf Construction, commissioning and characterisation of the PETALO-2 prototype}. 
\begin{itemize}
\item Construction of two LXSC6 cells: characterisation and choice of SiPMs, design of DBs, production of DBs, construction of SiPM HV modules, assembly and test (Q1/Q3-16).  
\item Engineering design of two LXSC6 modules and their respective cryostats (first quarter of 2016, noted as Q1-16). 
\item Construction of two LXSC6 modules and their respective cryostats (Q2-16).
\item Commissioning of PETALO-2 (Q3-16). This will require the availability of front-ed readout electronics, digitisation and slow control developed by subproject ASIC for PETALO-2.
\item Demonstration of the energy resolution and spacial resolution of the LXSC (Q4-16). 
\item Study of the performance of several configurations (LXSC2, LXSC3, LXSC6) to decide the optimal configuration for PETALO-10 (Q1-17). 
\item Operation of PETALO-2 inside the magnetic field of the NMR research apparatus at La Fe. Optimisation of operation and imaging in magnetic field. This is a common objective with subproject IMG (Q2-17). 
\item Demonstration of coincidence resolution time (CRT) between the two LXSC of PETALO-2 (Q3-17). 
\item Characterisation of photoelectric and multi-site, fully contained Compton 
events (Q4-17). 
\end{itemize}
\item {\bf Construction, commissioning and characterisation of the PETALO-10 small animal PET in a non-clinical environment}. 
\begin{itemize}
\item Construction of 10 LXSC modules, after validating the optimal configuration (probably LXSC2 or LXSC3) for PETALO-10 (Q2/Q3-17). 
\item Construction of the PETALO-10 cryostat  and gas system (Q1/Q3-2017).
\item Commissioning of PETALO-10 at IFIC (Q4-2017). This will require the availability of front-ed readout electronics, digitisation and slow control developed by subproject ASIC for PETALO-10.
\end{itemize}
\end{enumerate}
