\paragraph{Objectives of the IMG subproject.}
The specific objectives of the IMG subproject are:

\begin{enumerate}
\item {\bf Characterisation and study of performance of PETALO-10  in a clinical environment}. 
\begin{itemize}
\item Definition of clinical requirements (since PETALO-10 will be a medical device working with small animals, it will need to pass several quality and safety requirements to be used in a clinical environment. This will be done in parallel with the commissioning of PETALO-10 at IFIC (Q4-2017).
\item Operation of PETALO-10 with small animals. Development of imaging software to reconstruct PET images. Characterisation of the sensitivity of the device. This objective is common with subproject DET, and will be carried out by a team including scientists from both groups (Q1/Q2-18).
\end{itemize}
\item {\bf Operation and optimisation of  PETALO-10 in a NMR environment.}. 
\begin{itemize}
\item Validation of operation in intense magnetic field. Notice that PETALO-2 will have operated previously in magnetic field and thus validation of PETALO-10 should be straight forward (Q3-18).   
\item NMR images acquisition, which involves the development of protocols for the acquisition of images with combined NMR and PET data (Q3-2017).
\end{itemize} 
\item {\bf Image processing and reconstruction}. This is a major objective of the IMG group and will span the duration of the whole project
\begin{itemize}
\item Development of a full Monte Carlo simulation of PETALO-10. This is a common objective with DET suprobject (Q1/Q3-16)
\item Development of the software for PET imaging (filtered back projection and interactive techniques, display of acquired images) using Monte Carlo Data (Q4-16/Q1-17).
\item Testing of imaging software with PETALO-2 data (Q1/Q2-17).
\item Development of the software for registration and fusion of the NMR and PET using different techniques (segmentation, atlas-based) for the generation of attenuation maps in the PET images correction (Q1/Q4-17 using MC data and Q1/Q4-18 using PETALO-10 data).    
\end{itemize} 
\end{enumerate}
